Using Fundamental Measure Theory to Treat the Correlation Function of the Inhomogeneous Hard-Sphere Fluid

### 2012-08-17 papers/contact/paper.tex
plots look much prettier now!  number of small changes made to them.  Got rid of test particle section in paper and first to appendix subsections Tested everything on node06.

\subsection{Test-particle result}

Here we discuss comparison of the correlation function calculated via
both Monte Carlo and the test-particle approach (see
Figures~\ref{fig:inner-4-10} and~\ref{fig:inner-4-40}).

@@

@@

\subsection{Expressions for $\beta\frac{\delta A_{HS}}{\delta n_3(\mathbf{r}')}$, etc. for the White Bear Mark I free energy $A_{HS}$}

  First, let's rewrite the free energy in terms of a smaller set of weighted densities

  \begin{align}
    A_{HS} &= \int \left\{
    -n_0 \ln\left( 1 - n_3\right)
    + \frac{n_1 n_2 - \mathbf{n}_{V1} \cdot\mathbf{n}_{V2}}{1-n_3}
    + (n_2^3 - 3 n_2 \mathbf{n}_{V2} \cdot \mathbf{n}_{V2}) \frac{
      n_3 + (1-n_3)^2 \ln(1-n_3)
    }{
      36\pi n_3^2(1-n_3)^2
    }
    \right\}
  \end{align}

Taking derivatives we have

  \begin{align}
    \frac{\delta A_{HS}}{\delta n_3(\mathbf{r}')} &=
    \frac{n_0(\mathbf{r}')}{1 - n_3(\mathbf{r}')}
    + \frac{n_1n_2 - \mathbf{n}_{V1}\cdot\mathbf{n}_{V2}}{(1 -
      n_3(\mathbf{r}'))^2}
    - \frac{n_2^3 -
      3n_2\mathbf{n}_{V2}\cdot\mathbf{n}_{V2}}{36\pi}\left(
    \frac{n_3^2-5n_3+2}{n_3^3(1-n_3)^3} + 2\frac{\ln(1-n_3)}{n_3^3}
    \right)
    \\
    \frac{\delta A_{HS}}{\delta n_2(\mathbf{r}')} &=
    \frac{n_1}{1-n_3}
    + 3(n_2^2 - \mathbf{n}_{V2}\cdot\mathbf{n}_{V2})\frac{n_3 +
      (1-n_3)^2\ln(1-n_3)}{
      36\pi n_3^2(1-n_3)^2
    }
    \\
    \frac{\delta A_{HS}}{\delta n_1(\mathbf{r}')} &= \frac{n_2}{1-n_3}
    \\
    \frac{\delta A_{HS}}{\delta n_0(\mathbf{r}')} &=
    -\ln\left( 1 - n_3\right) \\
    \frac{\delta A_{HS}}{\delta \mathbf{n}_{V2}(\mathbf{r}')} &=
    \frac{\mathbf{n}_{V1}}{1-n_3}
    - 6 n_2 \mathbf{n}_{V2} \frac{n_3 +
      (1-n_3)^2\ln(1-n_3)}{
      36\pi n_3^2(1-n_3)^2
    }    \\
    \frac{\delta A_{HS}}{\delta \mathbf{n}_{V1}(\mathbf{r}')} &=
    \frac{\mathbf{n}_{V2}}{1-n_3} \\
  \end{align}

\subsection{Expressions for $\beta\frac{\delta A_{HS}}{\delta n_3(\mathbf{r}')}$, etc. for the White Brear Mark II free energy $A_{HS}$}

Similarly to the White Bear I case we first write

\begin{align} 
A_{HS} &= \int \left\{
    -n_0 \ln\left(1 - n_3\right)
    + \left(1 + \frac{1}{9}n_3^2 \phi_2(n_3)\right)   \frac{n_1 n_2 - \mathbf{n}_{V1} \cdot\mathbf{n}_{V2}}{1-n_3}
    + \left(1 - \frac{4}{9}n_3\phi_3(n_3)\right)\frac{n_2^3 - 3 n_2 \mathbf{n}_{V2} \cdot \mathbf{n}_{V2}}{24\pi (1-n_3)^2}
    \right\}
\end{align}
 where
 \begin{align}
   \phi_2 &= \left(6n_3 - 3n_3^2 + 6(1-n_3)\ln(1-n_3)\right)\frac{1}{n_3^3}\\
   \phi_3 &= \left(6n_3 - 9n_3^2 + 6n_3^3 + 6(1-n_3)^2 \ln(1-n_3)\right)\frac{1}{4n_3^3}
 \end{align}
For the following derivitives we have
\begin{align}
   \frac{\delta \phi_2}{\delta n_3} &= \left((-6+4n_3)\ln(1-n_3) - 6n_3 + n_3^2\right)\frac{3}{n_3^4}\\
   \frac{\delta \phi_3}{\delta n_3} &= \left(-6n_3 + 5n_3^2 + (-2n_3^2 + 8n_3 -6)\ln(1-n_3)\right)\frac{3}{4n_3^4}
 \end{align}
And using these
\begin{align}
  \frac{\delta A_{HS}}{\delta n_3} &= \psi _1 + \psi _2 + \psi _3
\end{align}
where
\begin{align}
  \psi_1 &= \frac{n_0}{1-n_3}\\
  \psi_2 &= \frac{n_1n_2 - \mathbf{n}_1\cdot \mathbf{n}_2}{1-n_3}\left(\frac{2}{9}n_3\phi_2 + \frac{1}{9}n_3^2\frac{\delta \phi_2}{\delta n_3}\right) + \left(1 + \frac{1}{9}n_3^2\phi_2\right)\frac{n_1n_2 - \mathbf{n}_1\cdot \mathbf{n}_2}{(1-n_3)^2}\\
  \psi_3 &= \frac{n_2^3 - 3n_2\mathbf{n}_2 \cdot \mathbf{n}_2}{24\pi(1-n_3)^2}\left(-\frac{4}{9}\phi_3 - \frac{4}{9}n_3\frac{\delta \phi_3}{\delta n_3}\right) + 2\left(1 - \frac{4}{9}n_3\phi_3\right)\frac{n_2^3 - 3n_2\mathbf{n}_2 \cdot \mathbf{n}_2}{24\pi(1-n_3)^3} 
\end{align}
We also have
\begin{align}
  \frac{\delta A_{HS}}{\delta n_2} &= (1 + \frac{1}{9}n_3^2\phi_2)\frac{n_1}{1-n_3} + (1 - \frac{4}{9}n_3\phi_3)\frac{3n_2^2 - 3\mathbf{n}_2 \cdot \mathbf{n}_2}{24\pi(1 - n_3)^2}\\
  \frac{\delta A_{HS}}{\delta n_1} &= (1 + \frac{1}{9}n_3^2\phi_2)\frac{n_2}{1 - n_3}\\
  \frac{\delta A_{HS}}{\delta n_0} &= -\ln(1 - n_3)\\
  \frac{\delta A_{HS}}{\delta \mathbf{n}_1} &= -(1 + \frac{1}{9}n_3^2 \phi_2)\frac{\mathbf{n}_2}{1 - n_3}\\
  \frac{\delta A_{HS}}{\delta \mathbf{n}_2} &= -(1 + \frac{1}{9}n_3^2\phi_2)\frac{\mathbf{n}_1}{1 - n_3} 
  - (1 - \frac{4}{9}n_3\phi_3)\frac{6n_2\mathbf{n}_2}{24\pi(1 - n_3)^2}
\end{align}

@@

>>>>

%% \subsection{Test-particle result}

%% Here we discuss comparison of the correlation function calculated via
%% both Monte Carlo and the test-particle approach (see
%% Figures~\ref{fig:inner-4-10} and~\ref{fig:inner-4-40}).

@@

%% \begin{figure}
%%   \includegraphics[width=\columnwidth]{figs/test-particle-10}
%%   \caption{DFT and monte-carlo nA compared with averaged test particle data with bulk filling
%%     fraction of 0.1.}
%%   \label{fig:test-particle-10}
%% \end{figure}

%% \begin{figure}
%%   \includegraphics[width=\columnwidth]{figs/test-particle-40}
%%   \caption{DFT and monte-carlo nA compared with averaged test particle data with bulk filling
%%     fraction of 0.4.}
%%   \label{fig:test-particle-40}
%% \end{figure}

@@

@@

%% \subsection{Expressions for $\beta\frac{\delta A_{HS}}{\delta n_3(\mathbf{r}')}$, etc. for the White Bear Mark I free energy $A_{HS}$}

%%   First, let's rewrite the free energy in terms of a smaller set of weighted densities

%%   \begin{align}
%%     A_{HS} &= \int \left\{
%%     -n_0 \ln\left( 1 - n_3\right)
%%     + \frac{n_1 n_2 - \mathbf{n}_{V1} \cdot\mathbf{n}_{V2}}{1-n_3}
%%     + (n_2^3 - 3 n_2 \mathbf{n}_{V2} \cdot \mathbf{n}_{V2}) \frac{
%%       n_3 + (1-n_3)^2 \ln(1-n_3)
%%     }{
%%       36\pi n_3^2(1-n_3)^2
%%     }
%%     \right\}
%%   \end{align}

%% Taking derivatives we have

%%   \begin{align}
%%     \frac{\delta A_{HS}}{\delta n_3(\mathbf{r}')} &=
%%     \frac{n_0(\mathbf{r}')}{1 - n_3(\mathbf{r}')}
%%     + \frac{n_1n_2 - \mathbf{n}_{V1}\cdot\mathbf{n}_{V2}}{(1 -
%%       n_3(\mathbf{r}'))^2}
%%     - \frac{n_2^3 -
%%       3n_2\mathbf{n}_{V2}\cdot\mathbf{n}_{V2}}{36\pi}\left(
%%     \frac{n_3^2-5n_3+2}{n_3^3(1-n_3)^3} + 2\frac{\ln(1-n_3)}{n_3^3}
%%     \right)
%%     \\
%%     \frac{\delta A_{HS}}{\delta n_2(\mathbf{r}')} &=
%%     \frac{n_1}{1-n_3}
%%     + 3(n_2^2 - \mathbf{n}_{V2}\cdot\mathbf{n}_{V2})\frac{n_3 +
%%       (1-n_3)^2\ln(1-n_3)}{
%%       36\pi n_3^2(1-n_3)^2
%%     }
%%     \\
%%     \frac{\delta A_{HS}}{\delta n_1(\mathbf{r}')} &= \frac{n_2}{1-n_3}
%%     \\
%%     \frac{\delta A_{HS}}{\delta n_0(\mathbf{r}')} &=
%%     -\ln\left( 1 - n_3\right) \\
%%     \frac{\delta A_{HS}}{\delta \mathbf{n}_{V2}(\mathbf{r}')} &=
%%     \frac{\mathbf{n}_{V1}}{1-n_3}
%%     - 6 n_2 \mathbf{n}_{V2} \frac{n_3 +
%%       (1-n_3)^2\ln(1-n_3)}{
%%       36\pi n_3^2(1-n_3)^2
%%     }    \\
%%     \frac{\delta A_{HS}}{\delta \mathbf{n}_{V1}(\mathbf{r}')} &=
%%     \frac{\mathbf{n}_{V2}}{1-n_3} \\
%%   \end{align}

%% \subsection{Expressions for $\beta\frac{\delta A_{HS}}{\delta n_3(\mathbf{r}')}$, etc. for the White Brear Mark II free energy $A_{HS}$}

%% Similarly to the White Bear I case we first write

%% \begin{align} 
%% A_{HS} &= \int \left\{
%%     -n_0 \ln\left(1 - n_3\right)
%%     + \left(1 + \frac{1}{9}n_3^2 \phi_2(n_3)\right)   \frac{n_1 n_2 - \mathbf{n}_{V1} \cdot\mathbf{n}_{V2}}{1-n_3}
%%     + \left(1 - \frac{4}{9}n_3\phi_3(n_3)\right)\frac{n_2^3 - 3 n_2 \mathbf{n}_{V2} \cdot \mathbf{n}_{V2}}{24\pi (1-n_3)^2}
%%     \right\}
%% \end{align}
%%  where
%%  \begin{align}
%%    \phi_2 &= \left(6n_3 - 3n_3^2 + 6(1-n_3)\ln(1-n_3)\right)\frac{1}{n_3^3}\\
%%    \phi_3 &= \left(6n_3 - 9n_3^2 + 6n_3^3 + 6(1-n_3)^2 \ln(1-n_3)\right)\frac{1}{4n_3^3}
%%  \end{align}
%% For the following derivitives we have
%% \begin{align}
%%    \frac{\delta \phi_2}{\delta n_3} &= \left((-6+4n_3)\ln(1-n_3) - 6n_3 + n_3^2\right)\frac{3}{n_3^4}\\
%%    \frac{\delta \phi_3}{\delta n_3} &= \left(-6n_3 + 5n_3^2 + (-2n_3^2 + 8n_3 -6)\ln(1-n_3)\right)\frac{3}{4n_3^4}
%%  \end{align}
%% And using these
%% \begin{align}
%%   \frac{\delta A_{HS}}{\delta n_3} &= \psi _1 + \psi _2 + \psi _3
%% \end{align}
%% where
%% \begin{align}
%%   \psi_1 &= \frac{n_0}{1-n_3}\\
%%   \psi_2 &= \frac{n_1n_2 - \mathbf{n}_1\cdot \mathbf{n}_2}{1-n_3}\left(\frac{2}{9}n_3\phi_2 + \frac{1}{9}n_3^2\frac{\delta \phi_2}{\delta n_3}\right) + \left(1 + \frac{1}{9}n_3^2\phi_2\right)\frac{n_1n_2 - \mathbf{n}_1\cdot \mathbf{n}_2}{(1-n_3)^2}\\
%%   \psi_3 &= \frac{n_2^3 - 3n_2\mathbf{n}_2 \cdot \mathbf{n}_2}{24\pi(1-n_3)^2}\left(-\frac{4}{9}\phi_3 - \frac{4}{9}n_3\frac{\delta \phi_3}{\delta n_3}\right) + 2\left(1 - \frac{4}{9}n_3\phi_3\right)\frac{n_2^3 - 3n_2\mathbf{n}_2 \cdot \mathbf{n}_2}{24\pi(1-n_3)^3} 
%% \end{align}
%% We also have
%% \begin{align}
%%   \frac{\delta A_{HS}}{\delta n_2} &= (1 + \frac{1}{9}n_3^2\phi_2)\frac{n_1}{1-n_3} + (1 - \frac{4}{9}n_3\phi_3)\frac{3n_2^2 - 3\mathbf{n}_2 \cdot \mathbf{n}_2}{24\pi(1 - n_3)^2}\\
%%   \frac{\delta A_{HS}}{\delta n_1} &= (1 + \frac{1}{9}n_3^2\phi_2)\frac{n_2}{1 - n_3}\\
%%   \frac{\delta A_{HS}}{\delta n_0} &= -\ln(1 - n_3)\\
%%   \frac{\delta A_{HS}}{\delta \mathbf{n}_1} &= -(1 + \frac{1}{9}n_3^2 \phi_2)\frac{\mathbf{n}_2}{1 - n_3}\\
%%   \frac{\delta A_{HS}}{\delta \mathbf{n}_2} &= -(1 + \frac{1}{9}n_3^2\phi_2)\frac{\mathbf{n}_1}{1 - n_3} 
%%   - (1 - \frac{4}{9}n_3\phi_3)\frac{6n_2\mathbf{n}_2}{24\pi(1 - n_3)^2}
%% \end{align}
